SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-01-24 scipy-1.0/paper.tex
Add brief description + citation of NumPy in first paragraph of intro.

SciPy is a library of numerical routines for the Python programming
language, providing the fundamental building blocks for modeling and
solving scientific problems.  For example, when LIGO, the Laser
Interferometer Gravitational-Wave Observatory, recently announced the
discovery of gravitational waves, their published Python analysis
scripts imported three different SciPy submodules: signal processing,
interpolation, and input/output.  SciPy has routines for solving
classes of generic problems such as optimization, integration,
interpolation, eigenvalues, and linear systems.  It also provides
specialized data structures, such as sparse arrays and k-dimensional
trees.  SciPy is built on top of NumPy, and is itself the foundation
upon which higher level scientific libraries, including scikit-learn\cite{pedregosa2011scikit}
and scikit-image\cite{vanderwalt2014scikit}, are built.

>>>>

SciPy is a library of numerical routines for the Python programming
language, providing the fundamental building blocks for modeling and
solving scientific problems.  For example, when LIGO, the Laser
Interferometer Gravitational-Wave Observatory, recently announced the
discovery of gravitational waves, their published Python analysis
scripts imported three different SciPy submodules: signal processing,
interpolation, and input/output.  SciPy has routines for solving
classes of generic problems such as optimization, integration,
interpolation, eigenvalues, and linear systems.  It also provides
specialized data structures, such as sparse arrays and k-dimensional
trees. SciPy is built on top of NumPy\cite{vanderwalt2011numpy,Oliphant-2015},
which provides array data structures and related fast numerical routines.
SciPy is itself the foundation upon which higher level scientific libraries,
including scikit-learn\cite{pedregosa2011scikit}
and scikit-image\cite{vanderwalt2014scikit}, are built.
